---
title: "HW1_zs2539"
output: github_document
chunk_output_type: console
---

# Problem 1 Solution

The dataset penguins includes three specices located in three islands during 2007-2009, 344 samples in total, describing their bill depth and length, flipper length, body mass and sex.
```{r setup, include=FALSE}
data("penguins", package = "palmerpenguins")
library(ggplot2)
library(dplyr)
```

## The size of the dataset is as follows

- Number of Rows
```{r}
nrow(penguins)
```

- Number of Columns
```{r}
ncol(penguins)
```

## Mean of flipper length in mm
```{r}
mean(penguins$flipper_length_mm,na.rm = T)
```

## Scatterplot of Flipper length-Bill Length by Species 
```{r}
FBplot1 = ggplot(data = penguins, mapping = aes(x = bill_length_mm, y = flipper_length_mm, colour = species)) + geom_point()
FBplot1
```

## Export the scatterplot to the project directory
```{r}
ggsave("p8105_hw1_zs2539.pdf",FBplot1)
```

# Problem 2 Solution

## Create the data frame comprised of a required random sample, with vectors including logical, character and factor.
```{r}
set.seed(1)

example_df = tibble(
  vec_numeric = rnorm(10),
  vec_char = c("n1", "n2", "n3", "n4", "n5", "n6", "n7", "n8", "n9", "n10"),
  vec_logical = vec_numeric > 0,
  vec_factor = factor(c("High","Medium","High","Medium","High","Medium", "Medium", "Low", "Low", "Low"))
)
```

## Now take the mean of each variable
```{r}
mean(example_df$vec_numeric,na.rm = T)
mean(example_df$vec_char,na.rm = T)
mean(example_df$vec_logical,na.rm = T)
mean(example_df$vec_factor,na.rm = T)
```

In summary, character and factor vectors do not work, while numeric and logical vectors work.

## Now convert those required vectors above to numeric
```{r eval = FALSE}
as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```
We can see that

- The range of logical vector is {0,1} only, so the mean is 0.6 by computation above.
- Factor vector is valued by natural number if converted, and cannot be computed directly before conversion.
- Character vector converted to numeric is still NA.